---
title: "modeltime"
output: html_notebook
---

```{r}
library(readr)
census_starter <- read_csv("GoDaddy/godaddy-microbusiness-density-forecasting/census_starter.csv")
train <- read_csv("GoDaddy/godaddy-microbusiness-density-forecasting/train.csv")
test <- read_csv("GoDaddy/godaddy-microbusiness-density-forecasting/test.csv")
```


# Combine train and test sets
```{r}
raw <- bind_rows(train, test) %>%
  arrange(cfips, row_id) %>%
  #reset index
  rownames_to_column() %>%
  mutate(index = 1:n()) %>%
  select(-rowname) %>%
  select(row_id, cfips, first_day_of_month, microbusiness_density) %>%
  set_names(c("id", "cfips", "date", "density"))
```

# Create nested time series tibble
```{r}
nested_raw <- raw %>%
  nest_timeseries(
    .id_var = cfips,                #grouping by cfips
    .length_actual = 39,            #defines the 39 months of actual data
    .length_future = 8              #defines the 8 months to forecast after
  ) %>%
  split_nested_timeseries(
    .length_test = 2                #uses the last 2 months of actual data to test
  )
```

## Step 1 Create tidymodels workflow

## Prophet
```{r}
rec_prophet <- recipe(density ~ date, extract_nested_train_split(nested_raw))

wflw_prophet <- workflow() %>%
  add_model(
    prophet_reg("regression") %>%
      set_engine("prophet")
  ) %>%
  add_recipe(rec_prophet)
```

## XGBoost
```{r}
rec_xgb <- recipe(density ~ ., extract_nested_train_split(nested_raw)) %>%
  step_timeseries_signature(date) %>%
  step_rm(date) %>%
  step_zv(all_predictors()) %>%
  step_dummy(all_nominal_predictors(), one_hot = TRUE)

wflw_xgb <- workflow() %>%
  add_model(
    boost_tree("regression") %>%
      set_engine("xgboost")
    ) %>%
  add_recipe(rec_xgb)
```


# Step 2 Nested Modeltime Tables

```{r}
nested_modeltime_tbl <- modeltime_nested_fit(
  # Nested data
  nested_data = nested_raw,
  
  # Add workflows
  wflw_prophet,
  wflw_xgb
)

nested_modeltime_tbl
```

## Logged Attributes
```{r}
nested_modeltime_tbl %>%
  extract_nested_test_accuracy() %>%
  table_modeltime_accuracy(.interactive = F)
```

## Extract nested test forecast
```{r eval=FALSE, include=FALSE}
nested_modeltime_tbl %>%
  extract_nested_test_forecast() %>%
  group_by(id) %>%
  plot_modeltime_forecast(
    .facet_ncol = 2,
    .interactive = FALSE
  )
```

## Extract nested error logs
```{r}
nested_modeltime_tbl %>%
  extract_nested_error_report()
```

# Select the best
```{r}
best_nested_modeltime_tbl <- nested_modeltime_tbl %>%
  modeltime_nested_select_best(
    metric                = "rmse",
    minimize              = TRUE,
    filter_test_forecasts = TRUE
  )
```

## Extract nested best model report
```{r}
best_nested_modeltime_tbl %>%
  extract_nested_best_model_report()
```

## Extract nested best test forecasts
```{r eval=FALSE, include=FALSE}
best_nested_modeltime_tbl %>%
  extract_nested_test_forecast() %>%
  group_by(id) %>%
  plot_modeltime_forecast(
    .facet_ncol = 2,
    .interactive = FALSE
  )
```

# Step 5 Refitting and Future Forecast
Now that we have all the best models in hand, we can make future forecasts by refitting the models to the full dataset

```{r}
nested_modeltime_tbl <- best_nested_modeltime_tbl %>%
  modeltime_nested_refit(
    control = control_nested_refit(verbose = TRUE)
  )
```

## Extract nested future forecast
```{r eval=FALSE, include=FALSE}
nested_modeltime_tbl %>%
  extract_nested_future_forecast() %>%
  group_by(id) %>%
  plot_modeltime_forecast()
```

